
```{r setup_user,echo=FALSE, message=FALSE,warning=FALSE}
# This is based on the file microcosm_datalogger_visualisation_v9.Rmd, adapted for more general use.
expt <- "2014-5-23"
expt_name = "martin1"
max_cycle_number <- 80
min_cycle_number <- 3
verbose <- FALSE

data_dir <- "D:/Dropbox/sourcetree/fluxan/data"
output_dir <- "output"

source("R/cycle_table_builder.R")

pt_base <- paste("Microcosm expt ",expt,". ", sep="")
# load libraries
library(ggplot2)
library("reshape2")
```

Microcosm carbon flux experiment `r expt`
===================================================================
This script analyses the datalogger file from a _single_ experimental run, and summarises the results in the exported cycle table. The cycle tables from individual runs are designed to be combined to allow a complete experimental analysis to be performed once all the runs are complete. This can be done in a separate script or by import of the cycle tables to other analysis software.

 
```{r setup_info, echo=FALSE}
cat("Script version: ",script_version,
    ".\nCore mass file: ", core_mass_file,
    ".\nSave cycle table: ", save_cycle_table,
    ".\nMax cycle: ", max_cycle_number,
    ".\nMin cycle: ",min_cycle_number)
cat("Start time: ",as.character(d$time[1]),
    "\nEnd time: ",as.character(d$time[nrow(d)]),
    "\nRef gas conc:",ref_gas_conc,
    "\nTime zone: ",tz,
    "\nFactor mapping file: ",mapping_file,
    "\nTiming file: ",timings_file,
    "\nInfiles: ", infiles)

    if(length(core_mass_file)>0) {
      print(core_mass_relative[,1:5])
      cat("water added at ",as.character(time_of_water_addition))
      }
```



```{r core_mass,fig.width=10, fig.height=6,echo=FALSE,message=FALSE,warning=FALSE}
if(length(core_mass_file)>0) {
      plot_title <- paste(pt_base,"\nEstimated core mass change")
      ggplot(subset(d, (IRGA_conn%in%core_names)) ,aes(x=time_elapsed,y=water_content_estimate,colour=factor(IRGA_conn))) + geom_point() + labs(title = plot_title) + facet_wrap(~IRGA_conn,ncol=1) + theme_bw()
} 

```



```{r fig.width=14, fig.height=14,echo=FALSE,message=FALSE,warning=FALSE}

plot_title <- paste(pt_base,"Raw CO2 data by cycle number.")
d.chambers <- subset(d,IRGA_conn!="ND"&IRGA_conn!="ambient"&IRGA_conn!="ref_gas"&cycle!=0)
d.chambers_ambient <- subset(d,IRGA_conn!="ND"&IRGA_conn!="ref_gas")

ggplot(d.chambers,aes(x=conn_timer_sec,y=IRGA_CO2)) + geom_line(size=0.5, aes(col=IRGA_conn,linetype=light)) + labs(title = plot_title) + facet_wrap(~cycle) + scale_y_continuous(limits=c(200,800)) + theme_bw()

```


### Environmental control data check
```{r plot_env_data,fig.width=14, fig.height=10,echo=FALSE,message=FALSE,warning=FALSE}
library(scales)

plot_title <- paste(pt_base,"Raw CO2 data by source.")
ggplot(d.chambers_ambient, aes(x=time, y=IRGA_CO2)) + geom_line(size=0.5, aes(col=IRGA_conn,linetype=light),position = position_jitter(w = 500, h = 0)) + facet_wrap(~IRGA_conn,ncol=1) + scale_y_continuous(limits=c(200,800)) + labs(title = plot_title) + theme_bw()

# Disabled temporarily 
#plot_title <- paste(pt_base,"Temperatures.")
#d.m <- melt(d,measure.vars=c(temp_sensor_col_names,"ref_temp","ref_temp2"))
#ggplot(d.m, aes(x=time, y=value)) + geom_line(size=0.5,aes(col=variable,linetype=light),position = position_jitter(w = 500, h = 0)) + scale_y_continuous(limits=c(5,30)) + labs(title = plot_title) + theme_bw()
#
plot_title <- paste(pt_base,"Humidity.")
d.m <- melt(d,measure.vars=c('IRGA_Humidity','ref_humidity'),na.rm=TRUE,)
ggplot(d.m, aes(x=time, y=value)) + geom_line(size=0.5,aes(col=IRGA_conn,linetype=light),position = position_jitter(w = 500, h = 0)) + facet_wrap(~variable,ncol=1) + labs(title = plot_title) + theme_bw()

plot_title <- paste(pt_base,"Air pressure.")
d.m <- melt(d,measure.vars=c('IRGA_Pressure','ref_pressure'))
ggplot(d.m, aes(x=time, y=value)) + geom_point(size=2,aes(col=IRGA_conn,linetype=light),position = position_jitter(w = 500, h = 0)) + facet_wrap(~variable,ncol=1) + labs(title = plot_title) + theme_bw()


```


```{r Cycle_analysis,warning=FALSE, fig.width=14, fig.height=9,echo=FALSE,message=FALSE}
#, eval=FALSE
if(length(cycle_numbers)>0) {
  
  plot_title <- paste(pt_base,"CO2 flux per cycle")
  print(    
    ggplot(cycle_table,aes(cycle_date_time,CO2_flux,colour=core,shape=light)) + geom_point(size=5) + labs(title = plot_title) + theme_bw() + scale_y_continuous(name="CO2 flux (mg C m-2 hr-1)") + theme(axis.title.x = element_text(size=20), axis.text.x  = element_text(size=16), axis.title.y = element_text(size=20), axis.text.y  = element_text(size=16), legend.text=element_text(size=18))  + scale_shape_manual(values = c(21,19,22)) 
        )
  
  plot_title <- paste(pt_base,"Chamber temperature")
  print(
    ggplot(cycle_table,aes(cycle_date_time,mean_temperature,shape=light,colour=core,)) + geom_point(size=5) + labs(title = plot_title) + theme_bw() + scale_y_continuous(name="chamber temp") + theme(axis.title.x = element_text(size=20), axis.text.x  = element_text(size=16), axis.title.y = element_text(size=20), axis.text.y  = element_text(size=16), legend.text=element_text(size=18))  + scale_shape_manual(values = c(21,19,22)) 
        )  
 
  
    plot_title <- paste(pt_base,"Period identification")
   print(   
    ggplot(cycle_table, aes(cycle_date_time,period,colour=period)) +   geom_point(size=3) + labs(title = plot_title) + theme_bw() + theme(axis.title.x = element_text(size=20), axis.text.x  = element_text(size=16), axis.title.y = element_text(size=20), axis.text.y  = element_text(size=16), legend.text=element_text(size=18))  
        ) 
  
    plot_title <- paste(pt_base,"CO2 flux per period")
  print(    
    ggplot(cycle_table[!is.na(cycle_table$period),],aes(core,CO2_flux,fill=period)) + geom_boxplot() + labs(title = plot_title) + theme_bw() + scale_y_continuous(name="CO2 flux (mg C m-2 hr-1)") + theme(axis.title.x = element_text(size=20), axis.text.x  = element_text(size=16), axis.title.y = element_text(size=20), axis.text.y  = element_text(size=16), legend.text=element_text(size=18)) 
    ) 

      plot_title <- paste(pt_base,"CO2 flux per factor by period")
  print(    
    ggplot(cycle_table[!is.na(cycle_table$period)&!is.na(cycle_table$factor),],aes(factor,CO2_flux,fill=period)) + geom_boxplot() + labs(title = plot_title) + theme_bw() + scale_y_continuous(name="CO2 flux (mg C m-2 hr-1)") + theme(axis.title.x = element_text(size=20), axis.text.x  = element_text(size=16), axis.title.y = element_text(size=20), axis.text.y  = element_text(size=16), legend.text=element_text(size=18)) 
    ) 
  
  # this plot is meaningless without the dry/wet factors so only make it if we have that info
  if(time_of_water_addition) {
    plot_title <- paste(pt_base,"CO2 flux summary")
    ggplot(cycle_table,aes(factor(core),CO2_flux,colour=core,fill=period)) + geom_boxplot() + labs(title = plot_title) + facet_wrap(~factor1) + theme_bw()
    
    plot_title <- paste(pt_base,"CO2 flux summary (wet cycles only)")
    ggplot(subset(cycle_table,factor1=="wet"),aes(factor(core),CO2_flux,fill=core)) + geom_boxplot() + labs(title = plot_title) + facet_wrap(~period) + theme_bw()
    
  }

# end of IF check for sensible cycle numbers
} else {
  cat("Not enough cycles available to analyse")
}

```


